Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plot

  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_manual(values = colcases) + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

@@

scores_full %>%
  ggplot(aes(y = interval_score, x = horizon, 
             fill = model, color = model)) +
  geom_boxplot(outlier.shape = 21, coef = 1.5, 
               width=0.5, alpha = 1, 
               position = position_dodge2(width = 0.5)) + 
  # geom_line(data = means, 
  #           aes(group = model, y = meanval, color = model), 
  #           position = position_dodge2(width = 0.5), 
  #           size = 2) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_brewer(palette = "Accent") + 
  geom_point(data = means, 
             mapping = aes(y = meanval, fill = model),
             color = "black",
             # fill = "red",
             shape = 21,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
    geom_point(data = means, 
             mapping = aes(y = medianval, fill = model),
             color = "black",
             # fill = "red",
             shape = 22,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
  scale_fill_brewer(palette = "Accent") + 
  scale_y_log10() + 
  facet_wrap( ~ location_target, scales = "free") + 
  theme(legend.position = "bottom")

>>>>

  scores_over_time_deaths <- scores_target_forecastdate[horizon == i & target_type == "death"] %>%
    scores_over_time_plot(y = "interval_score") + 
    scale_color_manual(values = coldeaths) + 
    annotate('rect', xmin = min(forecast_dates$full_hub_period) + 14,
             xmax = max(forecast_dates$death_not_scored) + 14,
             ymin = 0,
             ymax = Inf, fill = "grey10", alpha = 0.1) + 
    labs(y = "WIS rel. to baseline", x = "Date")

@@

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    # geom_density_ridges(aes(fill = model, color = NA),
    #                     rel_min_height = 0.005,
    #                     scale = 0.9,
    #                     # jittered_points = TRUE,
    #                     # position = position_points_jitter(width = 0.05, height = 0),
    #                     point_size = 1.5,
    #                     point_shape = 21,
    #                     #point_shape = '|',
    #                     point_alpha = 1,
    #                     alpha = 0.3) +
    ggdist::stat_dots(aes(color = model)) + 
    ggdist::stat_pointinterval(point_interval = mean_qi, size = 3, shape = 16, fill = "black", .width = NA) + 
    ggdist::stat_pointinterval(point_interval = median_qi, size = 3, shape = 15, fill = "black", .width = NA) + 
        facet_wrap(~ target_type, ncol = 1, scales = "free") + 
    theme(plot.margin=unit(c(0,0.4,0,0),"cm")) +
    # geom_density_ridges(quantile_lines=TRUE,
    #                     quantile_fun=function(x,...) mean(x), 
    #                     linetype = "dotted", 
    #                     alpha = 0, 
    #                     scale = 0.9, 
    #                     rel_min_height = 0.01) +
    scale_fill_manual(values = coldeaths) + 
    scale_color_manual(values = coldeaths) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL)) + 
    theme_light()
}

@@

scores_full %>%
  ggplot(aes(y = interval_score, x = horizon, 
             fill = model, color = model)) +
  geom_boxplot(outlier.shape = 21, coef = 1.5, 
               width=0.5, alpha = 1, 
               position = position_dodge2(width = 0.5)) + 
  # geom_line(data = means, 
  #           aes(group = model, y = meanval, color = model), 
  #           position = position_dodge2(width = 0.5), 
  #           size = 2) +
  # theme(panel.background = element_rect(fill = "#e1f0fe")) +
  scale_color_manual(values = coldeaths) + 
  scale_fill_manual(values = coldeaths) + 
  geom_point(data = means, 
             mapping = aes(y = meanval, fill = model),
             color = "black",
             # fill = "red",
             shape = 21,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
    geom_point(data = means, 
             mapping = aes(y = medianval, fill = model),
             color = "black",
             # fill = "red",
             shape = 22,
             size = 2,
             position = position_dodge2(width = 0.5)) + 
  scale_y_log10() + 
  facet_wrap( ~ location_target, scales = "free") + 
  theme(legend.position = "bottom")
